### 2017-04-06 paper/evaluation.tex
pass on eval

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.  We automatically parsed
\Fix{X} build files and we used the same approach to classify the
parsed configurations as in our previous analysis. Initially, we
noticed that our approach was unable to infer the parallel mode in
some projects because these projects do not declare a static value in
some parameters (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
it is required to inform additional parameters to enable the parallel
mode in the command line (\eg, \CodeIn{mvn test
-Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
NEGATIVES if we considered this $\rightarrow$}To handle this case, we
considered all valid values for the parameter.

We found ten projects that use parallelism using this methodology.
Compared to the set of projects listed in Figure~\ref{tab:speedup}, we
found two new projects, namely: \CodeIn{Google Cloud\Comment{
    Platform} DataflowJavaSDK} (using configuration C3) and
\CodeIn{Mapstruct} (using configuration \ForkSeq{}).  Curiously, we
also found that project \CodeIn{Jcabi} was not detected using this
methodology.  That happened because \Mar{please, explain why}.
Considering the static and dynamic methods together, we found a total
of 11 distinct projects using parallelism, corresponding to the union
of the two subject sets.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}

>>>>

%% Recall that some projects can use parallel execution that is only
%% activated when developers pass certain parameters to the build
%% process. For instance, it is possible to create in Maven multiple
%% configurations in the same build file and select dynamically which one
%% should be used.

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can ocurr when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.

Overall, we found, using this methodology, ten projects that use
parallelism.  Compared to the set of projects listed in
Figure~\ref{tab:speedup}, we found two new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration C3) and \CodeIn{Mapstruct} (using configuration
\ForkSeq{}).  Curiously, we also found that project \CodeIn{Jcabi} was
not detected using this methodology.  That happened because this
project loads its \emph{pom.xml} file from a jar file that we did not
check.  Considering the static and dynamic methods together, we found
a total of 11 distinct projects using parallelism, corresponding to
the union of the two subject sets.

\vspace{1ex}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}
\vspace{1ex}
